2.02-dev released on November 16, 2003

Contributors looking for a mission:

\begin{itemize}
\item just do an egrep on \char`\"{}TODO\char`\"{} or \char`\"{}XXX\char`\"{} and see what's there\end{itemize}


CURRENT RELEASE NOTES:

\begin{itemize}
\item This is a developer release, indicated by the \char`\"{}-dev\char`\"{} suffix on the version string. We believe the core interfaces to be stable, but some portions of the API may still need significant modification. Thus, binary/source compatibility may be broken from one developer release to the next. In particular the version numbering rules specified at\end{itemize}


{\tt http://apr.apache.org/versioning.html}

do not apply to developer releases.

RELEASE SHOWSTOPPERS:

CURRENT VOTES:

TODO:

\begin{itemize}
\item Get env/ (Apache::Test) tests to work for --with-apache2-src option.\end{itemize}


\begin{itemize}
\item Bring Perl documentation up to speed.\end{itemize}


\begin{itemize}
\item Write parser/hook API documentation.\end{itemize}


\begin{itemize}
\item Add XForms logic to the mfd parser.\end{itemize}


\begin{itemize}
\item symbol exports files:\begin{enumerate}
\item aix needs .exp files\end{enumerate}
\end{itemize}


OPEN ISSUES:

\begin{itemize}
\item Should we bundle an apr-based \char`\"{}application/xml\char`\"{} parser? If so, how should we parse the xml data into an apr\_\-table?\end{itemize}


\begin{itemize}
\item How should the Perl API work in a CGI context? Will users need to preload an \char`\"{}CGI environment\char`\"{} module before loading Request.so or Cookie.so?\end{itemize}


\begin{itemize}
\item Figure out how to bundle a CPAN release.\end{itemize}


BUGS:

XXX

WISH LIST:

\begin{itemize}
\item I [joes] wish folks would contribute some glue code for one of these:\end{itemize}


\begin{itemize}
\item php,\item Rivet,\item mod\_\-dtcl,\item mod\_\-python,\item mod\_\-jk,\item tomcat,\item mod\_\-ruby,\item mod\_\-parrot.\end{itemize}
